Kimbee: A Speech Therapy Application For Children

### 2015-03-09 Paper/paper.tex
fixed

\begin{figure*}[t]
  \centering
  \includegraphics[keepaspectratio, width=\textwidth]{tech_figure.png}
  \caption{Left: AAA. Middle: BBB. Right: CCC.}
  \label{fig:tech}
\end{figure*}

@@

We will now discuss the implementation details of each of the systems that make up {\em Kimbee}.

@@

[Game Implementation Details Here]

>>>>

\begin{figure*}[t]
  \centering
  \includegraphics[keepaspectratio, width=\textwidth]{tech_figure.png}
  \caption{Left: The Therapist Portal, the user system of the therapist. Middle: The Central Server, hosts the recordings and facilitates interactions. Right: The Kimbee Game, interactive game that allows practice of speech for children. }
  \label{fig:tech}
\end{figure*}

@@

We will now discuss the implementation details of each of the systems that make up {\em Kimbee}. This project is made up of many components. In particular we will discuss the three main systems: the Server, the Game, and the Therapist Portal. From a high level, the Game and the Therapist Portal are thinly interconnected to the Server via HyperText Transfer Protocol (HTTP).

@@
